Will Kamala Harris will win the 2024 Presidential election

### 2024-11-04 paper/paper.qmd
Added image
captions

```{r, fig.height= 2.5}
#| echo: false
#| warning: false
#| message: false
#| label: fig-supportstate
#| fig-cap: "Distribution of Support Percentage by State"

@@

```{r, fig.width= 6, fig.height= 2}
#| echo: false
#| warning: false
#| message: false
#| label: fig-supportWP
#| fig-cap:  "Support Percentage for Harris by State since Harris declared as Candidate for Wisconsin and Pennsylvania"

@@

```{r, fig.width= 6, fig.height= 2}
#| echo: false
#| warning: false
#| message: false
#| label: fig-supportAM
#| fig-cap:  "Support Percentage for Harris by State since Harris declared as Candidate"

@@

```{r, fig.width= 7, fig.height= 2.5}
#| echo: false
#| warning: false
#| message: false
#| label: fig-supportGNN
#| fig-cap:  "Support Percentage for Harris by State since Harris declared as Candidate"

@@

```{r, fig.width= 6, fig.height= 2}
#| echo: false
#| warning: false
#| message: false
#| label: fig-supportpollsters
#| fig-cap: "Variation in Harris's Support Percentage Across Pollsters Over Time"

@@

```{r}
#| echo: false
#| warning: false
#| message: false
#| label: fig-modelGANM
#| fig-cap: "Poll predictions of Arizona, Geogria, Michigan, North Carolina"

@@

ggplot(subset_up, aes(x = end_date_num, y = median_prob, color = state)) +
  geom_line(alpha = 0.5) +  
  geom_smooth(method = "gam", formula = y ~ s(x, bs = "cs", k = 10), se = FALSE) +
  labs(
    x = "Days Since First Poll",
    y = "Predicted Probability"
  ) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  facet_wrap(~ state) +
  theme(legend.position = "none")

@@

Without considering the swing states and if we assume all the other states will vote as expected Kamala Harris has a slight lead of 226 electoral votes to Donald Trump's 219. Now, if we take the 43 combined votes of Arizona, Georgia, and North Carolina, and add it to Trumps tally. While allocate Nevada, Michigan, Pennsylvania, and Wisconsin's votes to Harris which sum up to 50 electoral votes. This totals to a Democratic victory for Kamala Harris at 276 votes to Donald Trump's 262, we have come to the conclusion that Kamala Harris is likely to win the upcomming United States election by 14 electoral votes.

>>>>

```{r, fig.height= 2.5}
#| echo: false
#| warning: false
#| message: false
#| label: fig-supportstate
#| fig-cap: "Distribution of Support Percentage by State for Harris vs. Trump"

@@

```{r, fig.width= 6, fig.height= 2}
#| echo: false
#| warning: false
#| message: false
#| label: fig-supportWP
#| fig-cap:  "Predicted Support Percentage for Harris Over Time in Pennsylvania and Wisconsin Since Candidacy Declaration"

@@

```{r, fig.width= 6, fig.height= 2}
#| echo: false
#| warning: false
#| message: false
#| label: fig-supportAM
#| fig-cap: "Predicted Support Percentage for Harris Over Time in Arizona and Michigan Since Candidacy Declaration"

@@

```{r, fig.width= 7, fig.height= 2.5}
#| echo: false
#| warning: false
#| message: false
#| label: fig-supportGNN
#| fig-cap:  "Predicted Support Percentage for Harris Over Time in Georiga, Nevada, and North Carolina Since Candidacy Declaration"

@@

```{r, fig.width= 5.5, fig.height= 2.5}
#| echo: false
#| warning: false
#| message: false
#| label: fig-supportpollsters
#| fig-cap: "Variation in Harris's Support Percentage Across Pollsters Since Harris' Candidacy Declaration "

@@

```{r}
#| echo: false
#| warning: false
#| message: false
#| label: fig-modelGANM
#| fig-cap: "Predicted Probability of Support for Harris Over Time in Arizona, Georgia, Michigan, and North Carolina Since Harris' Candidacy Declaration"

@@

ggplot(subset_up, aes(x = end_date_num, y = median_prob, color = state)) +
  geom_line(alpha = 0.5) +  
  geom_smooth(method = "gam", formula = y ~ s(x, bs = "cs", k = 10), se = FALSE) +
  labs(
    x = "Days Since First Poll",
    y = "Predicted Probability"
  ) +
  theme_minimal() +
  theme(axis.text.x = element_text(hjust = 1)) +
  facet_wrap(~ state) +
  theme(legend.position = "none")

@@

Without considering the swing states and if we assume all the other states will vote as expected Kamala Harris has a slight lead of 226 electoral votes to Donald Trump's 219. Now, if we take the 43 combined votes of Arizona, Georgia, and North Carolina, and add it to Trumps tally. While allocate Nevada, Michigan, Pennsylvania, and Wisconsin's votes to Harris which sum up to 50 electoral votes. This totals to a Democratic victory for Kamala Harris at 276 votes to Donald Trump's 262, we have come to the conclusion that Kamala Harris is likely to win the upcomming United States election by 14 electoral votes. Below we have added a makeup of what we believe the election to look like in an image @270towin:

::: {.cell}
![Predicted Electoral Votes for the 2024 US Election ](../other/images/Election_map.png){fig-align="center" width="50%"}
:::
